---
title: "SIMPLE_LINEAR_REGRESSION"
output: html_notebook
---

SET WORKING DIRECTORY
```{r}
getwd()
#setwd()
```

IMPORT DATASET
```{r}
dataset = read.csv('Salary_Data.csv')
#dataset = dataset[, 2:3]
```

SPLIT DATASET INTO TRAINING AND TEST SET
```{r}
# install.packages('caTools')

library(caTools)
set.seed(123)
split = sample.split(dataset$Salary, SplitRatio = 2/3)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)

```

CHECK THE SPLIT DATASET FOR ROWS AND COLUMNS
```{r}
nrow(training_set)
nrow(test_set)
```

# - - - - - - - - - - - - - - - - - - -
# FEATURE SCALING Need to be done only if required.
# Feature Scaling
# training_set = scale(training_set)
# test_set = scale(test_set)
# - - - - - - - - - - - - - - - - - - -

FITTING SIMPLE LINEAR REGRESSION ON OUR TRAINING SET
```{r}
regressor = lm(formula = Salary ~ YearsExperience,
               data = training_set)

summary(training_set)
summary(regressor)

# P-Value lesser then 5 means INDEPENDENT & DEPENDENT VARIABLE are HIGHLY CORRELATED, which is shows with 3 ***
```

PREDICTING THE TEST SET RESULTS
```{r}
y_pred = predict(regressor, newdata = test_set)
```

VISUALISING THE TRAINING SET RESULTS
```{r}
# library(ggplot2)

# We will follow a STEP-BY_STEP APPROACH
# 1. Plot all our observation | 2. Then REGRESSION LINE | 3. TITLE | 4. LABELS - X & Y

ggplot() +
  geom_point(aes(x = training_set$YearsExperience, y = training_set$Salary),
             colour = 'red') +
  geom_line(aes(x = training_set$YearsExperience, y = predict(regressor, newdata = training_set)),
            colour = 'blue') +
  ggtitle('Salary vs Experience (Training set)') +
  xlab('Years of experience') +
  ylab('Salary')

```

VISUALISING THE TEST SET RESULTS
```{r}
#library(ggplot2)

ggplot() +
  geom_point(aes(x = test_set$YearsExperience, y = test_set$Salary),
             colour = 'red') +
  geom_line(aes(x = training_set$YearsExperience, y = predict(regressor, newdata = training_set)),
            colour = 'blue') +
  ggtitle('Salary vs Experience (Test set)') +
  xlab('Years of experience') +
  ylab('Salary')

```
